Relationship between reproduction and evaluation

### 2024-10-25 pages/relationship_reproduction_evaluation.qmd
docs(discussion): add various TODO and ideas for discussion

@@

>>>>

TODO: Add somewhere in discussion comments about subjectivity and reproduction and how the nature of what is being plot and so on can impact - e.g. health economic costs and qalys look super similar, but when turn into incremental to calculate ICER and INMB, tiny different result in big changes.

@@

TODO: Find right place for this reflection: The test-run stage after making compendium helped us to spot run issues that I hadn't noticed, mainly from having not completely tested absolutely everything before pushing. For example, Hernandez et al. 2015, and there was at least one other example too. Shows importance of having someone else check things - easy to leave in small mistakes that mean it doesn't run.

TODO: Make a paper with STRESS specific reflections - so ensure these are incorporated in others, then have discussion page where I walk through STRESS and, based on what I have found, suggest what was helpful in framework, what was missing, and so on.

* Consider: which of my reflections pertain to what is in the article, v.s. what is in the repository - e.g. the scenarios being used is important in both - but mine is actually referring more to the repository, hence relevant to STARS more-so than STARS

TODO: Add reflection from doing evaluations that likely not perfect, can be hard to find things in a paper, may have made mistakes, did have second person check to try and help with this, but that is why it can be so helpful to actually provide a completed framework, that highlights key reporting points for a given study, and where to look, particularly as things get more complicated with appendices and prior papers to refer back to for information.

TODO: Limitation of this work, not reuse, although did sometimes dig into some more than other to figure out how to code scenarios, which is similar to scenarios, but for some could just stay top level. Hence, in many cases, can't truly say if information provided was sufficient for that deep understanding of what it is doing and so on.

TODO: Consider, would there be any relevant literature related to time spent to try and get someone elses code mentioned - like how Andy mentioned there would be a max amount of time that someone in the NHS would reasonably spend troubleshooting

TODO: Include reflection that here is what was helpful for reuse, but some aspects of things are not helpful for reuse, but are helpful for other purposes - e.g. validity checks - e.g. web applications.
